### 2015-06-19 manuscript/manuscript.tex
Avance articulo falta optimal algoritmo

\title{Intraday Forex rates forecasting using an online cointegration approach}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

@@

%A Vector Error Correction Model (VECM) is an econometric model which
%characterizes the joint dynamic behaviour of a set of cointegrated variables. It
%is said that two non-stationary time series are cointegrated if a linear
%combination of them exhibit a stationary behaviour. 
%
%Cointegration is commonly found in finance and it has been shown that
%introducing cointegration restrictions often improves forecasting. However,
%determining VECM parameters and how much of the historical data is useful for
%making a forecast is a computational challenge.  
%
%In this study, we propose a new version of VECM whose parameters are obtained
%adaptively using parallel computing taking into account the cointegrated
%behaviour of the time series. The methodology is tested using data of the
%Foreign Exchange (Forex) market. Numerical experiments show that our adaptive
%and parallel approach significantly improves execution times with respect to the
%common serial processing and forecasts are made before new data arrives.  
Vector error correction model (VECM) parameters are commonly obtained using the
ordinary least squares method. Since this parameters could be sensitive to the
data, this proposal is to get these parameters using ridge regression which
could lead to a better generalization capability. In order to give with a
real-time response, an online version of VECM (OVECM) is proposed. OVECM solves
VECM considering only a sliding window of historical data and therefore
better response times could be achieved.

\keywords{VECM \and Cointegration \and Forex \and MPI \and Parallel algorithm}

@@

\section{Introduction}
\label{sec:introduction}
VECM introduces the long-run relationship among a set of cointegrated variables
as an error correction term. VECM is a special case of the vector autorregresive
model (VAR) model. VAR model expresses future values as a linear combination of
variables past values.  However, VAR model cannot be used with non-stationary
variables, which is a common feature of financial assets. VECM is a linear model
but in terms of variable differences. If cointegration exists, variable
differences are stationary and they introduce an error correction term which
adjusts coefficients to bring the variables back to equilibrium. In finance,
many economic time series turn to be stationary when they are differentiated and
cointegration restrictions often improves forecasting~\cite{duy1998}. Therefore,
VECM has been widely adopted.

Both VECM and VAR model parameters are obtained using ordinary least squares
(OLS) method. OLS has two main problems: is sensitive to errors on input data
and involves many calculations. The former problem is commonly solved using
Ridge Regression (RR) \cite{hoerl1970} which introduces a regularization
parameter that leads to an unbiased estimation with better generalization
capability. The second problem of computational complexity depends on the number
of past values and observations considered.  Recently, online learning
algorithms have been proposed to solve problems with large data sets because of
their simplicity and their ability to update the model when new data is
available.

Our proposal is an online formulation of the VECM called Online VECM (OVECM)
based on consideration of only a sliding window of the historical data.  OVECM
introduces matrix optimizations in order to reduce the number of operations and
also takes into account the fact that cointegration vector space doesn't
experience large changes with small changes in the input data. Moreover, OVECM
uses RR instead of OLS to obtain VECM parameters. Our method is later tested using four
currency rates from the foreign exchange market with a frequency of 10 seconds.
Model effectiveness is focused on out-of-sample forecast rather than in-sample
fitting.  This criteria allows the OVECM prediction capability to be expressed
rather than just explaining data history. Our method performance is compared
with its optimal offline algorithm.

@@

\subsection{Vector Autorregresive Models}\label{sec:varvec}

@@

The solution $\widehat{\mathbf{A}}$ to
equation~(\ref{eq:vareq}) can be obtained by the ordinary least squares (OLS)
method. $\widehat{\mathbf{X}}$ is the solution of the quadratic optimization problem
\begin{equation*}
\widehat{\mathbf{X}} = \underset{\mathbf{X}}{\text{Arg\;min}}
\|\mathbf{A}\mathbf{X}-\mathbf{B}\|_2^2
\end{equation*}
\noindent for which the solution $\widehat{\mathbf{X}}$ is well-known:
\begin{equation*}
\label{eq:MP}
\widehat{\mathbf{X}}=\mathbf{A}^{\!\!+}\,\mathbf{B}
\end{equation*}
\noindent where $\mathbf{A}^{\!\!+}$ is the Moore-Penrose pseudo-inverse
which, when $\mathbf{A}$ is full rank, can be written as follows: 
\begin{equation}
\label{eq:pseudoinverse}
\mathbf{A}^{\!\!+}= (\mathbf{A}^{\!\!\top} \mathbf{A})^{-1}\mathbf{A}^{\!\!\top} \, .
\end{equation}
when $\mathbf{A}$ is not full rank, i.e
$rank(\mathbf{A})=k <  n \leq m$, $\mathbf{A}^\top \mathbf{A}$ is
always singular and equation~(\ref{eq:pseudoinverse}) cannot be used.
More generally, the pseudo-inverse is best computed using the compact
singular value decomposition (SVD) of $\mathbf{A}$ which is:
\begin{equation*}
    \label{eq:compactsvd}
    \mathbf{A}=
    \mathbf{U_1}
    \boldsymbol \Sigma_1
    \mathbf{V}_1^{\top} \, .
\end{equation*}
Pseudo-inverse can then be written as follows:
\begin{equation*}
\label{eq:pseudoinversesvd}
\mathbf{A}^{\!\!+} = \mathbf{V}_1 \boldsymbol \Sigma_1^{-1} \mathbf{U}_1^\top \, .
\end{equation*}

@@

\section{Experimental results}
\label{sec:results}
\subsection{Data} \label{sec:unitroot}
%AVECM tests were carried out using four foreign exchange rates all related to
%USD: EURUSD, GBPUSD, USDCHF and USDJPY. This data was collected from the free
%database Dukascopy which gives access to the Swiss Foreign Exchange marketplace
%~\cite{Dukascopy2014}.
%
%The tests were done using 10-seconds frequency from ask prices which
%corresponded to 8640 data points per day from the 11th to the 15th of August
%2014. Since data datetimes were in GMT, opening market times for London, New
%York, Sidney and Tokyo corresponded with data points 1440, 3240, 6120 and 6840
%respectively. Our tests were made considering two hours after the opening time
%of the 13th of August. Therefore, in order to obtain these times, we added 2
%days and 2 hours to all the opening times ($2\times 8640 + 2 \times 360$) to obtain:
%19440, 21240, 24120 and 24840. We called offset to these times in
%table~\ref{tab:stats}, which allowed us to obtain performance at different
%times of the day.

@@

\begin{figure}[!ht]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.4\textwidth]{forexdata}
  \caption{10 seconds frequency forex data for EURUSD, GBPUSD and USDJPY}
  \label{fig:forexdata}
\end{figure}

\begin{figure}[!ht]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.4\textwidth]{distdata}
  \caption{Distribution of EURUSD, GBPUSD and USDJPY data}
  \label{fig:distdata}
\end{figure}

\begin{figure}[!ht]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.4\textwidth]{onlinecomparison}
  \caption{Cumulative loss of AAR, RR and OLS solutions for VECM against its optimal algorithm}
  \label{fig:onlinecomparison}
\end{figure}

\begin{figure}[!ht]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.4\textwidth]{RRcomparison}
  \caption{Cumulative loss RR VECM against its optimal algorithm using different $\lambda$ values}
  \label{fig:RRcomparison}
\end{figure}

\begin{figure}[!ht]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.4\textwidth]{AARcomparison}
  \caption{Cumulative loss AAR VECM against its optimal algorithm using different $\lambda$ values}
  \label{fig:AARcomparison}
\end{figure}

>>>>

\title{High frequency Intraday Forex rates forecasting using an online cointegration approach}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

@@

This research examines the cointegration relation between three mayor currency pairs (MCP) of the foreign exchange markets:  EURUSD, GBPUSD, USDCHF. Specifically, we used a modified version of the Vector error correction model (VECM) which parameters are updated online using a limited amount of historical data.
VECM parameters are commonly obtained using the
ordinary least squares (OLS) method. Our proposal is to solve VECM using Ridge regression (RR) and the Aggregating algorithm for regression (AAR) which could lead to a better generalisation capability rather than OLS. Both approaches together with OLS are compared against an optimal offline algorithm which is able to see the sequences in advance.
Our experiments were carried out using 10-seconds frequency Forex data and shows that RR and AAR approaches improve cumulative loss of OLS approach with respect to the optimal offline algorithm.

\keywords{VECM \and Cointegration \and Forex \and High frequency data \and Online algorithm}

@@

\section{Introduction}
\label{sec:introduction}

The relationships between financial time series are commonly studied. In particular, in some of them
it is possible to detect long-run relationships through to a cointegration analysis. Two or more non-stationary time series are said to be cointegrated if there exists a linear combination of them which is stationary.

Vector error correction model (VECM) introduces the long-run relationship among a set of cointegrated variables
as an error correction term. VECM is a special case of the vector autoregressive
model (VAR) model. VAR model expresses future values as a linear combination of
variables past values.  However, VAR model cannot be used with non-stationary
variables, which is a common feature of financial assets. VECM is a linear model
but in terms of variable differences. If cointegration exists, variable
differences are stationary and they introduce an error correction term which
adjusts coefficients to bring the variables back to equilibrium. In finance,
many economic time series (foreign exchange market rates for example) turns out to be stationary, when they are differentiated once ($I(1)$) and
cointegration restrictions applied on the model often improves forecasting~\cite{duy1998}. Therefore,
VECM has been widely adopted.

VECM parameters are obtained using ordinary least squares
(OLS) method \cite{golub1980}. OLS has two main problems: is sensitive to errors on input data
and involves many calculations. The former problem is commonly solved using
Ridge Regression (RR) \cite{hoerl1970} which introduces a regularisation
parameter that leads to an unbiased estimation with better generalisation
capability. The second problem of computational complexity depends on the number
of past values and observations considered.  Recently, online learning
algorithms have been proposed to solve problems with large data sets because of
their simplicity and their ability to update the model when new data is
available. We use an online version of the linear ridge regression and also a modification introduced by 
Vovk \cite{vovk2001} called the Aggregating algorithm regression (AAR), which is also known as Vovk-Azoury-Warmuth predictor ~\cite{azoury2001}.

Our proposal is an online formulation of the VECM called Online VECM (OVECM)
based on consideration of only a sliding window of the historical data.  OVECM parameters are obtained
via OLS, RR or AAR. A competitive analysis is done comparing its cumulative losses against the optimal offline algorithm.

In finance, little academic research has been done using high-frequency Forex
rates \cite{Bekiros2015}. Our proposal is tested using four
three mayor currency pairs (MCP) from the foreign exchange market:  Euro (EUR) to United States Dollar (USD) (EURUSD), British Pound (GBP) to
USD (GBPUSD) and USD to Swiss Franc (CHF) (USDCHF). We used samples with a frequency of 10 seconds.

This paper is organised as follows: section~\ref{sec:background} presents concepts of integration and cointegration, the VECM model and an online learning introduction, the OVECM algorithm is presented in section~\ref{sec:methodology}.
In section~\ref{sec:results} we describe the experiments carried out and their results. This section also includes a
description of the test data.  Section~\ref{sec:conclusions} contains the
conclusions and a discussion of future research.

@@

\subsection{Vector Error Correction Model}\label{sec:varvec}

@@

The solution $\widehat{\mathbf{A}}$ to
equation~(\ref{eq:vareq}) can be obtained by the ordinary least squares (OLS)
method. $\widehat{\mathbf{X}}$ is the solution of the quadratic optimization problem
\begin{equation*}
\widehat{\mathbf{X}} = \underset{\mathbf{X}}{\text{Arg\;min}}
\|\mathbf{A}\mathbf{X}-\mathbf{B}\|_2^2
\end{equation*}
\noindent for which the solution $\widehat{\mathbf{X}}$ is well-known:
\begin{equation*}
\label{eq:MP}
\widehat{\mathbf{X}}=\mathbf{A}^{\!\!+}\,\mathbf{B}
\end{equation*}
\noindent where $\mathbf{A}^{\!\!+}$ is the Moore-Penrose pseudo-inverse
which, when $\mathbf{A}$ is full rank, can be written as follows: 
\begin{equation}
\label{eq:pseudoinverse}
\mathbf{A}^{\!\!+}= (\mathbf{A}^{\!\!\top} \mathbf{A})^{-1}\mathbf{A}^{\!\!\top} \, .
\end{equation}
%when $\mathbf{A}$ is not full rank, i.e
%$rank(\mathbf{A})=k <  n \leq m$, $\mathbf{A}^\top \mathbf{A}$ is
%always singular and equation~(\ref{eq:pseudoinverse}) cannot be used.
%More generally, the pseudo-inverse is best computed using the compact
%singular value decomposition (SVD) of $\mathbf{A}$ which is:
%\begin{equation*}
%    \label{eq:compactsvd}
%    \mathbf{A}=
%    \mathbf{U_1}
%    \boldsymbol \Sigma_1
%    \mathbf{V}_1^{\top} \, .
%\end{equation*}
%Pseudo-inverse can then be written as follows:
%\begin{equation*}
%\label{eq:pseudoinversesvd}
%\mathbf{A}^{\!\!+} = \mathbf{V}_1 \boldsymbol \Sigma_1^{-1} \mathbf{U}_1^\top \, .
%\end{equation*}

\subsection{Ridge regression method}

In order to avoid the singularity of the matrix $\mathbf{A}^\top \mathbf{A}$, a regularisation term is introduced:

\begin{equation}
\label{eq:RRproblem} 
J(\mathbf{\mathbf{X}}) =  \| \mathbf{A}\mathbf{\mathbf{X}} - \mathbf{Y} \|_2^2  + \lambda
 \| \mathbf{\mathbf{X}}\| ^2
\end{equation}

\noindent which optimal solution $\mathbf{\mathbf{X}}_*$ is well known:

\begin{equation}
\label{eq:optsolRR}
\mathbf{\mathbf{X}}_*=(\mathbf{A}^\top \mathbf{A}+\lambda \mathbb{I})^{-1}\mathbf{A}^\top y \, ,
\end{equation}

\subsection{Online learning}
Online learning is a supervised machine learning framework that is useful when
we have sequential access to a sample only once.  This differs from the
classical batch learning, where there is an entire data set available and the
learner can build the internal model without any limits in accessing the data.
In batch learning, there is time enough to carefully analyse the dataset, build
large predictive models and combine them in a sophisticated way. However, when
execution time is critical and new data is required to be included in the model,
online learning algorithms are a better option.

In batch learning, the training phase is commonly a computationally expensive
process. Therefore, when new data arrives it can't be included easily to the
model. Moreover, it could happen that we won't have enough time to process the
new data before more data arrives. In online learning algorithms there is no
training phase, but the model is updated and evaluated at every time step. This
model updating is computationally less expensive than a training phase.
Online algorithms allow incremental learning by processing one instance at a
time. This is done updating the current model instead of building the model from
scratch.

Online learning is also useful when some past data may be irrelevant
or we want to improve computational efficiency. However, the use of less
historical data could affect accuracy.

The online learning framework was first introduced in the perceptron algorithm
\cite{rosenblatt58}. There are several other widely used online methods such as
passive-aggressive \cite{crammerETall2006}, stochastic gradient descent
\cite{zhang2004}, aggregating algorithm \cite{vovk2001} and the second order
perceptron \cite{cesa-bianchi2005}.  In \cite{cesa-bianchi2006} an in-depth
analysis of online learning is provided.

Algorithm~\ref{alg:onlinealg} shows the online learning algorithm structure:

\begin{algorithm}[ht]
\begin{algorithmic}[1]
    \STATE Receives input $\mathbf{x}_t$
    \STATE Makes prediction $\mathbf{\hat{y}}_t$
    \STATE Receives response $\mathbf{y}_t$
    \STATE Incurs loss $l_t(\mathbf{y}_t,\mathbf{\hat{y}}_t)$
\end{algorithmic}
\caption{Structure of a Learning System}
\label{alg:onlinealg}
\end{algorithm}

\noindent where $l$ is some loss function. Performance is later measured after
$T$ trials as:

\begin{equation*}
L_T = \sum_{t=1}^T l_t(\mathbf{y}_t,\mathbf{\hat{y}}_t)
\end{equation*}

Competitive analysis was designed for analysing the performance of an online algorithm compared with its optimal offline algorithm. An optimal offline algorithm can view the sequences of requests in advance. The effectiveness of an online algorithm \cite{sleator1985} may be measured by its competitive ratio which is the worst-case ratio of the online algorithm and the the optimal offline algorithm.

\subsection{Online Ridge Regression}

Online RR is the online formulation of the regularised Least Squares method
and is based on the following equivalent formulation of the RR optimal solution.

%Since 
%\begin{equation}
%\label{eq:notation}
%	\mathbf{A} = 
%\left[
%  \begin{tabular}{c>{$}c<{$}c}
%    --- & \mathbf{a}^{\top}_{1} & ---\\
%    --- & \mathbf{a}^{\top}_{2} & ---\\
%    & \vdots & \\
%    --- & \mathbf{a}^{\top}_{m} & ---
%  \end{tabular}
%\right]
%\quad \text{and} \quad
%\mathbf{B} =
%\left[
%  \begin{tabular}{c>{$}c<{$}c}
%    --- & \mathbf{b}_{1} & ---\\
%    --- & \mathbf{b}_{2} & ---\\
%    & \vdots & \\
%    --- & \mathbf{b}_{m} & ---
%  \end{tabular}
%\right]
%\end{equation}

Equation~(\ref{eq:optsolRR}) can also be written as:
\begin{eqnarray*}
\label{eq:RReapand}
\mathbf{\mathbf{X}}_{\text{ridge}}&=&(\mathbf{A}^\top \mathbf{A}+ \lambda
\mathbb{I})^{-1}\mathbf{A}^\top \mathbf{Y} \\
&=& \displaystyle \big (\sum_{t=1}^m
\mathbf{a}_t \mathbf{a}_t  ^\top + \lambda \mathbb{I}\big )^{-1}
\sum_{t=1}^m \mathbf{a}_t \mathbf{y}_t \, .
\end{eqnarray*}

Lets define $\displaystyle\mathbf{S}= \sum_{t=1}^m \mathbf{a}_t
\mathbf{a}_t  ^\top + \lambda \mathbb{I} $ and $\mathbf{W}=
\displaystyle\sum_{t=1}^m \mathbf{a}_t \mathbf{y}_t$, so the
algorithm~\ref{alg:RR} shows the iterative formulation:

\begin{algorithm}[H]
\begin{algorithmic}[1]
\REQUIRE $\,$ \\
$\{\mathbf{a}_1,\dots,\mathbf{a}_{m} \}$: $m$ input vectors \\
$\{\mathbf{y}_1,\dots,\mathbf{y}_{m} \}$: $m$ target vectors \\
$\lambda$: regularization parameter \\
\ENSURE  $\,$ \\
$\{f(\mathbf{a}_1),\dots,f(\mathbf{a}_{m}) \}$: model predictions \\
\STATE Initialize $\mathbf{S}=\lambda \mathbb{I}$
and $\mathbf{W}=0$
\FOR { $t = 1$ to $m$ }
	\STATE read new $\mathbf{a}_t$
	\STATE $\mathbf{X}=\mathbf{S}^{-1}\mathbf{W}$
	\STATE output prediction $f(\mathbf{a}_t) = \mathbf{X}^\top \mathbf{a}_t$
   	\STATE $\mathbf{S} = \mathbf{S} + \mathbf{a}_t \mathbf{a}_t^\top$
   	\STATE Read new $y_t$
    	\STATE $\mathbf{W} = \mathbf{W} + \mathbf{a}_t \mathbf{y}_t$
\ENDFOR
\end{algorithmic}
\caption{Online Ridge Regression}
\label{alg:RR}
\end{algorithm}

\subsection{The Aggregating Algorithm for Regression}

The AAR, proposed by~\cite{vovk2001} (also known as Vovk-Azoury-Warmuth predictor ~\cite{azoury2001}), is an application of the aggregating
algorithm to the problem of regression. The idea is introduce the new input
vector $\mathbf{x}_{m+1}$ to solve the model parameters:

\begin{equation}
\label{eq:AARexpand}
\mathbf{X}_{aar} = \displaystyle \big (\sum_{t=1}^{m+1}
\mathbf{a}_t \mathbf{a}_t  ^\intercal + \gamma \mathbb{I}\big )^{-1}
\sum_{t=1}^m \mathbf{a}_t \mathbf{y}_t \, .
\end{equation}

If we define $\displaystyle\mathbf{S}= \sum_{t=1}^{m+1} \mathbf{a}_t
\mathbf{a}_t  ^\intercal + \gamma \mathbb{I} $ and $\mathbf{W}=
\displaystyle\sum_{t=1}^m \mathbf{a}_t \mathbf{y}_t$, the
algorithm~\ref{alg:AAR} is slightly different to the algorithm~\ref{alg:RR}, 
which updated matrix $\mathbf{S}$ before making the prediction:

\begin{algorithm}[ht]
\begin{algorithmic}[1]
\REQUIRE $\,$ \\
$\{\mathbf{a}_1,\dots,\mathbf{a}_{m} \}$: $m$ input vectors \\
$\{\mathbf{y}_1,\dots,\mathbf{y}_{m} \}$: $m$ target vectors \\
$\lambda$: regularisation parameter \\
\ENSURE  $\,$ \\
$\{f(\mathbf{a}_1),\dots,f(\mathbf{a}_{m}) \}$: model predictions \\
\STATE Initialize $\mathbf{S}=\lambda \mathbb{I}$
and $\mathbf{W}=0$
\FOR { $t = 1$ to $m$ }
	\STATE read new $\mathbf{a}_t$
   	\STATE $\mathbf{S} = \mathbf{S} + \mathbf{a}_t \mathbf{a}_t^\intercal$
	\STATE $\mathbf{X}=\mathbf{S}^{-1}\mathbf{W}$
	\STATE output prediction $f(\mathbf{a}_t) = \mathbf{X}^\intercal \mathbf{a}_t$
   	\STATE Read new $\mathbf{y}_t$
    	\STATE $\mathbf{W} = \mathbf{W} + \mathbf{a}_t \mathbf{y}_t$
\ENDFOR
\end{algorithmic}
\caption{{\em The aggregating algorithm for regression}}
\label{alg:AAR}
\end{algorithm}

@@

\section{Experimental results}
\label{sec:results}
\subsection{Data} \label{sec:unitroot}

Experiments were run with data starting at 9:00 GMT of the 11th of August 2014,
which corresponds to the opening of the New York financial market.

%AVECM tests were carried out using four foreign exchange rates all related to
%USD: EURUSD, GBPUSD, USDCHF and USDJPY. This data was collected from the free
%database Dukascopy which gives access to the Swiss Foreign Exchange marketplace
%~\cite{Dukascopy2014}.
%
%The tests were done using 10-seconds frequency from ask prices which
%corresponded to 8640 data points per day from the 11th to the 15th of August
%2014. Since data datetimes were in GMT, opening market times for London, New
%York, Sidney and Tokyo corresponded with data points 1440, 3240, 6120 and 6840
%respectively. Our tests were made considering two hours after the opening time
%of the 13th of August. Therefore, in order to obtain these times, we added 2
%days and 2 hours to all the opening times ($2\times 8640 + 2 \times 360$) to obtain:
%19440, 21240, 24120 and 24840. We called offset to these times in
%table~\ref{tab:stats}, which allowed us to obtain performance at different
%times of the day.

@@

\begin{figure}[!ht]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.5\textwidth]{forexdata}
  \caption{10 seconds frequency forex data for EURUSD, GBPUSD and USDJPY}
  \label{fig:forexdata}
\end{figure}

\begin{figure}[!ht]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.5\textwidth]{distdata}
  \caption{Distribution of EURUSD, GBPUSD and USDJPY data}
  \label{fig:distdata}
\end{figure}

\begin{figure}[!ht]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.5\textwidth]{onlinecomparison}
  \caption{Cumulative loss of AAR, RR and OLS solutions for VECM against its optimal algorithm}
  \label{fig:onlinecomparison}
\end{figure}

\begin{figure}[!ht]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.5\textwidth]{RRcomparison}
  \caption{Cumulative loss RR VECM against its optimal algorithm using different $\lambda$ values}
  \label{fig:RRcomparison}
\end{figure}

\begin{figure}[!ht]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.5\textwidth]{AARcomparison}
  \caption{Cumulative loss AAR VECM against its optimal algorithm using different $\lambda$ values}
  \label{fig:AARcomparison}
\end{figure}

### 2015-06-19 src/4_OnlineLearning.tex
Avance articulo falta optimal algoritmo

In batch learning, the training phase is commonly a computationally expensive
process. Therefore, when new data arrives it can't be included easily to the
model. Moreover, it could happen that we won't have enought time to process the
new data before more data arrives. In online learning algorithms there is no
training phase, but the model is updated and evaluated at every time step. This
model updating is computationally less expensive than a training phase.
Online algorithms allow incremental learning by processing one instance at a
time. This is done updating the current model instead of building the model from
scratch.

@@

Competitive analysis was designed for analysing the performance of an online algorithm compared with its optimal offline algorithm. An optimal offline algorithm can view the sequences of requests in advance. The effectiveness of an online algorithm \cite{} may be measured by its competitive ratio which is the worst-case ratio of the online algorithm and the the optimal offline algorithm.

>>>>

In batch learning, the training phase is commonly a computationally expensive
process. Therefore, when new data arrives it can't be included easily to the
model. Moreover, it could happen that we won't have enough time to process the
new data before more data arrives. In online learning algorithms there is no
training phase, but the model is updated and evaluated at every time step. This
model updating is computationally less expensive than a training phase.
Online algorithms allow incremental learning by processing one instance at a
time. This is done updating the current model instead of building the model from
scratch.

@@

Competitive analysis was designed for analysing the performance of an online algorithm compared with its optimal offline algorithm. An optimal offline algorithm can view the sequences of requests in advance. The effectiveness of an online algorithm \cite{sleator1985} may be measured by its competitive ratio which is the worst-case ratio of the online algorithm and the the optimal offline algorithm.
